---
title: "Event counts"
output: html_document
---
Event counts for outcome of interest including analysis not run due to low event counts.

Time periods with less than or equal to 5 events have been marked as [Redacted] and the 'all post expo' variable which is a sum of all the time periods (excl. 'pre expo') has been updated to not include the [Redacted] counts.

Any results with redacted results will be at the top of the results file for easy review.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DT)
library(readr)
knitr::opts_knit$set(root.dir = gsub("/analysis","",getwd()))
```

## Compiled event counts

```{r, echo=FALSE, message=FALSE, warning=FALSE}
df=read_csv(paste0(output_dir,"/suppressed_compiled_event_counts_", event_name, ".csv"))
df %>%
    datatable(extensions = 'Buttons',
              options = list(dom = 'Blfrtip',
                             buttons = c('copy', 'csv', 'excel', 'pdf', 'print' ),
                             lengthMenu = list(c(50,-1),
                                               c(50,"All"))))
```


